---
title: "MI Calculaiton"
output: html_document
date: Dec-11-2024
author: Md Yousuf Ali
toc: false
---



```{r}
#| include=FALSE
library(DT)
library(data.table)
```

## Incidence

```{r}
#| include=FALSE
dt <- structure(list(SEX = structure(c("F", "F", "F", "F", "F", "F",
"F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F", "F",
"F"), label = "Sex"), Dose = c("HD", "HD", "HD", "HD", "HD",
"HD", "HD", "HD", "HD", "HD", "HD", "HD", "HD", "HD", "HD", "HD",
"HD", "HD", "HD", "HD"), MISPEC = structure(c("GLAND, ADRENAL",
"GLAND, ADRENAL", "GLAND, ADRENAL", "GLAND, ADRENAL", "GLAND, ADRENAL",
"GLAND, ADRENAL", "GLAND, ADRENAL", "GLAND, ADRENAL", "GLAND, ADRENAL",
"GLAND, ADRENAL", "GLAND, ADRENAL", "GLAND, ADRENAL", "GLAND, ADRENAL",
"GLAND, ADRENAL", "GLAND, ADRENAL", "GLAND, ADRENAL", "GLAND, ADRENAL",
"GLAND, ADRENAL", "GLAND, ADRENAL", "GLAND, ADRENAL"), label = "Specimen Material Type"),
    MISTRESC = c("HEMORRHAGE", "HEMORRHAGE", "HEMORRHAGE", "HEMORRHAGE",
    "HEMORRHAGE", "HEMORRHAGE", "HEMORRHAGE", "HEMORRHAGE", "HYPERTROPHY",
    "HYPERTROPHY", "HYPERTROPHY", "HYPERTROPHY", "HYPERTROPHY",
    "HYPERTROPHY", "HYPERTROPHY", "HYPERTROPHY", "HYPERTROPHY",
    "MINERALIZATION", "NECROSIS", "UNREMARKABLE"), MISEV = structure(c(4L,
    4L, 5L, 5L, 5L, 5L, 3L, 5L, 4L, 4L, 4L, 4L, 4L, 4L, 4L, 3L,
    4L, 4L, 4L, 1L), levels = c("0", "1", "2", "3", "4", "5"), class = c("ordered",
    "factor"))), class = c("data.table", "data.frame"), row.names = c(NA,
-20L))
```

As the middle step, we created a dataframe which have information like
animal SEX and Dose. Also all the MI(Microscopic Findings) domain data.
Let's start with some animals which were filter out by SEX, Dose and
MISPEC from the dataframe.

we get a group of 20 animals


```{r}
#| echo=FALSE
dt
```

Remove MISEV (Severity) for now

```{r}
#| include=FALSE
dt_f <- dt[, c(1,2,3,4)]
```

### Original Data

```{r}
#| echo=FALSE
dt_f
```

###  Count the animals in each group

```{r}
#| include=FALSE
dt_count <- dt_f[,.N,by=.(MISTRESC)]
```



```{r}
#| echo=FALSE
dt_count
```



```{r}
#| include=FALSE
dt_p <- data.table::copy(dt_f)
dt_p <- dt_p[,`:=`(n=.N) , by=.(MISTRESC)]
dt_p <- dt_p[!duplicated(dt_p)]
dt_p[,`:=`(percent=n/sum(n))]
```

### Find incidence rate/percent

```{r}
#| echo=TRUE
dt_p
```

### Sampling
#### Findings

```{r}
dt_p$MISTRESC
```

#### Incidance rate

```{r}
dt_p$percent
```

#### Sampling using R function

```{r}
#| include=TRUE
syn_percent <- sample(x=dt_p$MISTRESC,
                      size = 20, replace = TRUE,
                      prob = dt_p$percent)
```



```{r}
#| echo=FALSE
syn_percent
```

#### Incidence Count/Table

```{r}
#| include=FALSE
syn_p <- table(syn_percent)
```



```{r}
#| echo=FALSE
syn_p
```



```{r}
#| include=FALSE
kk <- data.frame(syn_p)
kk$MISTRESC <- kk$syn_percent
kk$N <- kk$Freq
kk$Freq <- NULL
kk$syn_percent <- NULL
syn_count <- kk
```



```{r}
#| include=FALSE
syn_count$MISTRESC <- as.character(syn_count$MISTRESC)
dt_org <- dt_f[,c(1,2,3,4)]
mistc <- NULL
for(i in 1:nrow(syn_count)){
misc <- syn_count[i,c('MISTRESC')]
count <- syn_count[i,c('N')]
val <- rep(misc,count)
mistc <- c(mistc,val)
}
dt_syn <- data.table::copy(dt_org)
dt_syn$MISTRESC_syn <- mistc
```



```{r}
#| echo=FALSE
dt_syn
```



```{r}
#| include=FALSE
dt_syn_p <- data.table::copy(dt_syn)
dt_syn_p <- dt_syn_p[,c(1,2,3,5)]
dt_syn_p <- dt_syn_p[,`:=`(n=.N) , by=.(MISTRESC_syn)]
dt_syn_p <- dt_syn_p[!duplicated(dt_syn_p)]
dt_syn_count <- data.table::copy(dt_syn_p)
dt_syn_p[,`:=`(percent=n/sum(n))]
```

### Original Count

```{r}
#| echo=FALSE
dt_count
```

### Synthetic Count

```{r}
#| include=FALSE
dt_count_syn <- dt_syn[,.N,by=.(MISTRESC_syn)]
```



```{r}
#| echo=FALSE
dt_count_syn
```

### Original Data

```{r}
#| echo=FALSE
dt_p
```

### Synthetic Data

```{r}
#| echo=FALSE
dt_syn_p
```

## Severity

```{r}
#| include=FALSE
dt_sev <- data.table::copy(dt)
dt_sev_org <- data.table::copy(dt)
dt_sev_org <- dt_sev_org[,c('SEX','Dose',
                            'MISPEC','MISTRESC','MISEV')]
dt_sev <- dt_sev[,c('SEX','Dose','MISPEC','MISTRESC',
                    'MISEV')]
```



```{r}
#| echo=FALSE
dt_sev
```

### Percent

```{r}
#| include=FALSE
dt_sev <- dt_sev[,c('SEX','Dose','MISPEC','MISEV')]
dt_sev <- dt_sev[,`:=`(n=.N),by=.(MISEV)][!duplicated(dt_sev)]
dt_sev[,`:=`(percent=n/sum(n))]
dt_sev$MISEV <- as.numeric(dt_sev$MISEV)
```



```{r}
#| echo=FALSE
dt_sev
```

for each of MISPEC (if not UNREMARKABLE)
find severity

```{r}
ll <- sample(dt_sev$MISEV, size = 1, replace = TRUE, prob = dt_sev$percent)
```

### synthetic

```{r}
#| include=FALSE
test <- c()
for(i in 1:nrow(dt)){
ll <- sample(dt_sev$MISEV, size = 1, replace = TRUE, prob = dt_sev$percent)
test <- c(test,ll)
}
```



```{r}
#| echo=FALSE
test
```



```{r}
#| include=FALSE
dt_synthetic <- data.table::copy(dt_sev_org)
dt_synthetic$MISEV_syn <- test
dt_synthetic$MISTRESC_syn <- mistc
dt_synthetic[MISTRESC_syn=='UNREMARKABLE',
                             `:=`(MISEV_syn=0)]
dt_synthetic <- dt_synthetic[,c('SEX','Dose','MISPEC',
                                'MISTRESC',
                                'MISEV',
                                'MISTRESC_syn',
                                'MISEV_syn')]
```

### Final Severity

```{r}
#| echo=FALSE
print(dt_synthetic)
```

NOTE: severity for UNREMARKBLE set 0 for MISEV_syn.

There are more steps involved which create the final
synthetic data but this is a simplified version(main idea) the way synthetic data created
